---
title: "Week 8 Lab"
author: "Quentin"
date: "March 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load the Packages

```{r}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)
library(ggplot2)
```

###Column Graph of Texas Oil Spills

```{r}
oil_spills <- read_csv("oil_spills.csv")
```


```{r}
df <- oil_spills %>%
  filter(`Accident State` == "TX" & `Accident Year` < 2017) %>% 
  group_by(`Accident Year`) %>% 
  summarise(Loss = sum(`Net Loss (Barrels)`))
```

```{r}
colnames(df) <- c("Year", "Loss")
```

```{r}
ggplot(df, aes(x = Year, y= Loss)) +
         geom_col()
```

```{r}
df_loc <- oil_spills %>%
  filter(`Accident State` == "TX" & `Accident Year` == 2016) %>%
  select(Latitude, Longitude, `Net Loss (Barrels)`)

colnames(df_loc) <- c("latitude", "longitude", "net_loss")

oil_sf <- st_as_sf(df_loc, coords = c("longitude", "latitude"), crs = 4326)

leaflet(oil_sf) %>%
  addTiles() %>%
  addMarkers()
```

## tmap plot with the Texas state shapefile

```{r}
states <- st_read(dsn = ".", layer = "states")

tex_border <- states %>% 
  filter(STATE_NAME == "Texas") %>% 
  st_transform(4326)

plot(tex_border)

tm_shape(tex_border) +
  tm_polygons() +
  tm_shape(oil_sf) +
  tm_dots(size = 0.3)
```


###Convert the data to spatial points patterns
(combination of the point data and the bounding window)

```{r}

spill_sp <- as(oil_sf, "Spatial")
spill_ppp <- as(spill_sp, "ppp")

tx_sp <- as(tex_border, "Spatial")
tx_owin <- as(tx_sp, "owin")

all_ppp <- ppp(spill_ppp$x, spill_ppp$y, window = tx_owin)

```

###A Density Plot:
```{r}
plot(density(all_ppp, sigma = 0.3))
```


###Quadrat Test for Spacial Evenness
Are oil spills evenly distributed throughout the state?

```{r}
oil_qt <- quadrat.test(all_ppp, nx = 5, ny = 5)
oil_qt

plot(all_ppp)
plot(oil_qt, add = TRUE, cex = 0.4)

```

###G-Function for Nearest Neighbor Analysis
```{r}
r <- seq(0,1, by = 0.01)

oil_gfun <- envelope(all_ppp, fun = Gest, r = r, nsim = 100)

ggplot(oil_gfun, aes(x = r, y = obs)) +
  geom_line(color = "black")+
  geom_line(aes(x = r, y = theo, color = "red"))

```
What this tells us is that our observed data has a higher proportion of point pairs with nearest neigbors at shorter distances compared to CSR data.
Units of x-axis (r) ???


### Nearest Neighbor Using the L-Function (same as Ripley's K, but standardized)
doing 20 simulations, but on your own you probably want to do more

```{r}

r2 <- seq(0,3, by = 0.5)

oil_lfun <- envelope(all_ppp, fun = Lest, r = r2, nsim = 20, global = TRUE)

ggplot(oil_lfun, aes(x = r2, y = obs)) +
  geom_line(color = "black")+
  geom_line(aes(x = r2, y = theo), color = "blue")

```

